---
title: "Hello R"
author: "Adam Guenoun"
date: "Data 2401"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The datasaurus_dozen file has 1846 rows, 3 columns, and 3 variables. The 3 variables are *dataset*, *x*, and *y*.

### Exercise 2

The correlation between x and y is -0.0645.

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

First, let's plot the data in the star dataset

```{r plot-star}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()

```


Next, let's calculate the correlation between `x` and `y` in this dataset.

```{r cor-star}
dino_data %>%
  summarize(r = cor(x, y))

```

The correlation coefficient for 'star' is -0.0630. Its correlation coefficient is extremely similar to 'dino', being only 0.0015 greater than 'dinos' coefficient of -0.0645.

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r plot-circle}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()


```

```{r cor-circle}
dino_data %>%
  summarize(r = cor(x, y))

```

The correlation coefficient of 'circle' is -0.0683. it is similar to 'dino's' coefficient of -0.0645, but has a minuscule increase in negative correlation.


### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)
